### 2013-11-20 regressionModelling.Rmd
perGini in the regression

model.names.multi.A = c("SB empty",
                      "SB individual",
                      "SB all",
                      "IB empty",
                      "IB individual",
                        "IB all")

htmlreg(list(soc.0,soc.1,soc.4,
            ind.0,ind.1,ind.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
```

>>>>

model.names.multi.A = c("SB empty",
                      "SB individual",
                      "SB all",
                      "IB empty",
                      "IB individual",
                        "IB all",
                        "SB perGini",
                        "IB perGini")

SBperGini <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
IBperGini <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        perGini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

htmlreg(list(soc.0,soc.1,soc.4,
            ind.0,ind.1,ind.4,
             SBperGini,IBperGini),
        custom.model.names = model.names.multi.A,
        #custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = TRUE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
```
